### 2015-05-06 Workshop2015/camera-ready/conclusions.tex
Final version reviewed to make sentences shorter

Current big data settings impose  to consider SLA and different data delivery models. We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-known solutions  adapted to these contexts. We are currently developing the strategies and algorithms sketched here applied to energy consumption applications and also to elections and political campaign data integration in order to guide decision making on campaign strategies.

>>>>

Current big data settings impose  to consider SLA and different data delivery models. We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-known solutions  adapted to these contexts. We are  developing  strategies and algorithms overviewed in this paper and applying them to energy consumption applications and to elections and political campaign data integration to guide decision making on campaign strategies.

### 2015-05-06 Workshop2015/camera-ready/incremental.tex
Final version reviewed to make sentences shorter

In our context, data are provided by services deployed on different clouds. 
In the example of the MOOC system presented above, several producers will supply equivalent content for a given period of time. 
They will be chosen with respect to the  preferences expressed by a consumer.

Consumers will specify queries as Datalog- or SQL-like programs including spatio-temporal attributes and preferences.
For instance, the following query $Q_1$: ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and are labeled as experts, where the total cost is less than 1 dollar, using only services that preserve their anonymity}''.

@@

%shows the general architecture of an SLA guided data integration system. 
%It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.

%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following lines describe how this query is evaluated according to our approach.

@@

%In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants. 
%Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g. cost, inscription, or exchange unit), and the time window in which they can produce contents. 
%Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content. 
%An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.

@@

%Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size. In other words, it  returns the cost of the data, as well as its  size and location.
The second method is used to engage to a data service (in our example a content data service) and will be used  if the service is retained for a composition to answer the query.

@@

Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week. Besides, she wishes to keep the content exchange private and she wants to order services by reputation. The maximum total cost will condition also the kind of privacy preserving algorithms that will be applied.

>>>>

In our context, data are provided by services deployed on different clouds. 
In the preivous   MOOC system example, several producers will supply equivalent content for a given period of time. 
They will be chosen with respect to the  preferences expressed by a consumer.

Consumers  specify queries as Datalog- or SQL-like programs including spatio-temporal attributes and preferences.
For instance, the following query $Q_1$: ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and are labeled as experts, where the total cost is less than 1 dollar, using only services that preserve their anonymity}''.

@@

@@

@@

%Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
For each service $e_i$, the first method returns the cost of the data (in our example, the cost of a given course (content)), as well as its  size and location,  and a required minimum size.  
The second method is used to engage to a data service (in our example a content data service) and will be used  if the service is retained for a composition to answer the query.

@@

Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week. Besides, she wishes to keep the content exchange private and she wants to order services by reputation. The maximum total cost will  also determine the kind of privacy preserving algorithms that will be applied.

### 2015-05-06 Workshop2015/camera-ready/queryRewriting.tex
Final version reviewed to make sentences shorter

Query rewriting is a well-known problem for databases.
It consists in transforming an abstract query into lower-level queries that can be answered by available databases.
%Query rewriting is guided by the schema of  abstract and concrete databases.
The answers to the lower level queries are combined in order to obtain the result.
The query rewriting problem can be generalized to the case of services:
The query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
Query rewriting techniques have been adapted to the context of data providing services~\cite{BBM10,ZLC11} as well as for general service compositions~\cite{CostaAMR13}. 
The latter case (\textit{i.e}, services that maintain and update information) is a generalization of the data provision case.
The general case requires considering the functional and non-functional aspects of the query and available services.
%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
%In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
%The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
%In the LAV approach, 
The rewriting process is guided by the specification of both the query to be rewritten and the available services.
%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
The solutions proposed are ranked and may be coded into concrete workflows.

The approach proposed in~\cite{CostaAMR13} which may be extended to the case of SLA-guided service-based data integration. 
%
%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
Let us consider the MOOC scenario, where people can participate on a content trading pool.
We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.

>>>>

Query rewriting 
%is a well-known problem for databases. It
 consists in transforming an abstract query into lower-level queries that can be answered by available databases.
%Query rewriting is guided by the schema of  abstract and concrete databases.
The answers to the lower level queries are combined in order to obtain the result.
The query rewriting problem can be generalized to the case of services:
The query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
Query rewriting techniques have been adapted to the context of data providing services~\cite{BBM10,ZLC11} as well as for general service compositions~\cite{CostaAMR13}. 
The latter case (\textit{i.e}, services that maintain and update information) is a generalization of the data provision case.
`%The general case requires considering the functional and non-functional aspects of the query and available services.
%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
%In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
%The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
%In the LAV approach, 
The rewriting process is guided by the specification of both the query to be rewritten and the available services.
%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
The solutions proposed are ranked and may be coded into concrete workflows that will be executed in one or several clouds by a special engine.

The approach proposed in~\cite{CostaAMR13} is being extended to the case of SLA-guided service-based data integration. 
%
%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
Let us consider the MOOC scenario, where people can participate on a content trading pool.
We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.

### 2015-05-06 Workshop2015/camera-ready/relwork.tex
Final version reviewed to make sentences shorter

%The agreed conditions should be explicit and quantifiable.
%They should be part of the contract between the client and the service provider.
%Their quantifiable nature makes it possible for the conditions to appear as non-functional requirement to be imposed to each individual service.
%SLA could concern all types of services on the cloud (IaaS, PaaS or SaaS).

%SLA compliance may be ensured by construction or may be monitored during the execution of the service.
%Monitoring SLAs is normally part of the infrastructure provided by the cloud.
%Service monitoring may incur in extra processing costs.

%SLA currently exploited in the cloud allows service providers and cloud clients to describe the amount of resources to be simultaneously used and also the conditions to use them.
%This limit may apply both for the service provider and the client (in the case of service invocation).

%Negotiating a SLA may be a difficult task.
%Indeed, 
SLA are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
From the user point of view, the interest is normally on \textit{service} delivery measures that are related with her QoS requirements like service availability, resilience, recovery time or cost.
The challenge is to couple technical and service delivery measures expressed in SLA in order to agree on the conditions in which they will be considered for executing tasks for a user. Existing works use matching and negotiation techniques for addressing this challenge.  
For instance,~\cite{5547150} 
proposes a bottom-up approach based on a cloud component that monitors technical measures, analyses and matches them to service delivery (high level) clauses expressed by the user.
\cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.
Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  
\cite{Ortiz:2013:VPS:2486767.2486772} proposes a set of templates to cloud users, each specifying the query type that can be executed with their tread-off in time and cost.  
The client  chooses among the proposed templates the one that best corresponds   to her requirements. \cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters, represented in RDF. RDF definitions are then converted into graph representations. An \textit{Induced Propagation Graph} is calculated from both models to establish correspondences.

@@

 Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, maybe because measures concern data services and not data itself.
Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources, whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).  
Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility. 
\cite{anisetti2014auctions} proposed an e-auctions based approach for matching services with requirements in multi-cloud settings. 
Our work aims at going further in the use of SLA for integrating data and it provides strategies to guide the whole data integration process.

>>>>

SLA are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
From the user point of view, the interest is normally on \textit{service} delivery measures that are related with her QoS requirements like service availability, resilience, recovery time or cost.
The challenge is to couple technical and service delivery measures expressed in SLA in order to agree on the conditions in which they will be considered for executing tasks for a user. Existing works use matching and negotiation techniques for addressing this challenge.  
For instance,~\cite{5547150} 
proposes a bottom-up approach based on a cloud component that monitors technical measures, analyses and matches them to service delivery (high level) clauses expressed by the user.
\cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.
Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  
\cite{Ortiz:2013:VPS:2486767.2486772} proposes a set of templates to cloud users, each specifying the query type that can be executed with their tread-off in time and cost.  
The client  chooses among the proposed templates the one that best corresponds   to her requirements. \cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters, represented in RDF. RDF definitions are then converted into graph representations. An \textit{Induced Propagation Graph} is calculated from both models to establish correspondences.

@@

 Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, in our opinion because measures concern data services and not data itself.
Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources. In contrast,  data integration in a multi-cloud context implies  expressing and enforcing multiple granularity constraints in different aspects of SLA (users, services, clouds and inter-cloud environments).  
Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility. 
\cite{anisetti2014auctions} proposed an e-auctions based approach for matching services with requirements in multi-cloud settings. 
Our work aims at going further in the use of SLA for integrating data and it provides strategies to guide the whole data integration process.
